Vulnerability Analysis of Container Images in Neuroimaging

### 2020-02-17 paper.tex
before meeting
after meeting

\begin{comment}
This work involves three experiments.
First experiment involves scanning
the images. We use three different scanners
to see if all are reporting same vulnerabilities or not. Second experiment involves updating
all these images and then rescanning. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.
\end{comment}

In this section, we present our study methodology. We first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. Later, we discuss 
various Linux distributions and their releases. Lastly, this section
provides a description of the scanning tools used.

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.
In Ubuntu launchpad database, for a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\

\noindent <release>\_<source-package>: <status> (<version/notes>) \\

The status can be any one of the following:

@@

In this section, we present and compare the scanning results of three scanners.

@@

\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports them.
4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair Scanner.

@@

\subsection{Effect Of Update}

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find the package manager inside the image and then update the image according to the package manager it finds.
When these images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2} shows the number of vulnerabilities that are detected by Anchore after updating these images.

\begin{figure*}[!htb]
        {\includegraphics[width=\textwidth]
        {Figures/afterupdatewithpackage.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}

>>>>

In this section, we present our study methodology.
This study involves three image scanning experiments.
First experiment involves scanning
the images. For that purpose, we use three different scanners. Second experiment involves updating
all these images and then rescanning them. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.

We first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. Later, we discuss 
various Linux distributions and their releases. Lastly, this section
provides a description of the three scanning tools used.

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.
In Ubuntu launchpad database, for a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
The status can be any one of the following:

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities and lastly, this section presents the effect of image size reduction on the
vulnerabilities.

@@

\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports them.
4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair Scanner.
Linux-kernel-headers are the headers files that only provide function names, its parameters, and its
return type.
The actual source code of these functions is present in the Linux kernel and not inside the image.
So, vulnerability detection in header files
is irrelevant in this case.

@@

\subsection{Effect Of Update}
\begin{comment}
The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find the package manager inside the image and then update the image according to the package manager it finds.
\end{comment}

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} compares the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
\begin{figure*}[!htb]
        {\includegraphics[width=\textwidth]
        {Figures/afterupdatewithpackage.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}
